\subsection{Agreement Tasks}
We construct six \emph{agreement tasks}: two for the ablation studies, with a single long-range dependency, and four number-agreement (NA) tasks for the nesting experiments, having two dependencies (Figure \ref{fig:design}). We give a short description of these tasks below. Table~\ref{tab:na-tasks-overview} provides an overview of all tasks. 

\input{tables/table_NA_tasks}

\paragraph{Tasks for the Ablation Experiments} For the ablation studies, we construct NA-tasks with a single long-range dependency across a prepositional phrase \citep{lakretz2019emergence}. To identify long-range number units, we use NounPP-number (Table~\ref{tab:na-tasks-overview}), in which the main subject and verb agree on grammatical number, and a second noun (attractor) can interfere during sentence processing. To identify long-range gender units, we use NounPP-gender, in which the main subject and a predicative adjective agree on gender, and an attractor having an opposite gender can interfere in the middle. 

\paragraph{Tasks for the Nesting Experiments} For the nesting experiments, we use four different NA-tasks. All tasks contain two subject-verb dependencies; they differ in terms of whether these dependencies are \emph{successive} or \emph{nested} and whether the embedded dependency is \emph{short-} or \emph{long-range}. Two subject-verb dependencies are \emph{successive} when the second noun occurs only after the first has been resolved. 
Such dependencies occur, for instance, in declarative sentences with a sentential complement, such as ``Il \textbf{ragazzo} \textbf{dice} che la \textit{donna conosce} il cane'' (``The \textbf{boy says} that the \emph{woman knows} the dog'').
In this example, the subject and verb are directly adjacent in both dependencies.
We thus call these dependencies \emph{short-range}, and the above sentence is an example of a sentence that could occur in the \emph{Short-Successive} NA-task. 
To create sentences that have a successive but \emph{long-range} subject-verb relationship, we increase the distance between the second noun and its corresponding verb by inserting a prepositional phrase in between: ``Il \textbf{ragazzo} \textbf{dice} che la \textit{donna} accanto al \underline{figlio} \textit{conosce} il cane' '(``The \textbf{boy says} that the \emph{woman} next to the \underline{son} \emph{knows} the dog''). For nested dependencies, we consider sentences with object-relative clauses, such as ``Il \textbf{ragazzo} che la \emph{figlia} \emph{ama} \textbf{conosce} il contadino'' (``The \textbf{boy} who the \emph{daughter} \emph{loves} \textbf{knows} the farmer'').
As the nested dependency in this sentence is short range, we call the corresponding number-agreement task \emph{Short-Nested} (note however that the main-clause dependency is long range). For \emph{Long-Nested}, we again use prepositional phrases to increase the distance between the subject and verb of the nested dependency: ``Il \textbf{ragazzo} che la \emph{figlia} vicino alla \underline{donna} \emph{ama} \textbf{conosce} il contadino'' (``The \textbf{boy} who the \emph{daughter} near the \underline{woman} \emph{loves} \textbf{knows} the farmer'').